A Hybrid Ensemble Learning Approach to Star-Galaxy Classification

### 2015-05-08 paper/main.tex
add stats affiliation to RJB

\author[E. J. Kim, R. J. Brunner \& M. Carrasco Kind]{
  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu}, Robert J.~Brunner$^2$,
  and Matias Carrasco Kind$^{2,3}$\\
$^1$Department of Physics, University of Illinois, Urbana, IL 61801 USA\\
$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA\\
$^3$National Center for Supercomputing Applications, Urbana, IL 61801 USA}

>>>>

\author[E. J. Kim, R. J. Brunner \& M. Carrasco Kind]{
  Edward J.~Kim$^1$\thanks{jkim575@illinois.edu},
  Robert J.~Brunner$^{2,3,4}$,
  and Matias Carrasco Kind$^{2,4}$\\
$^1$Department of Physics, University of Illinois, Urbana, IL 61801 USA\\
$^2$Department of Astronomy, University of Illinois, Urbana, IL 61801 USA\\
$^3$Department of Statistics, University of Illinois, Champaign, IL 61820 USA\\
$^4$National Center for Supercomputing Applications, Urbana, IL 61801 USA}
